Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-13 output/latex/manuscript.tex
supplementary material: rearrange LVs cell type figures to fix latex positioning
latex: add new lines in authors list
latex: add authors' affiliations

  \textbf{Milton Pividori}

@@

  Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA
  · Funded by The Gordon and Betty Moore Foundation GBMF 4552; The National Human Genome Research Institute (R01 HG010067); The National Human Genome Research Institute (K99HG011898); The Eunice Kennedy Shriver National Institute of Child Health and Human Development (R01 HD109765)

@@

  \textbf{Sumei Lu}
  Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA

@@

  \textbf{Binglan Li}

@@

  Department of Biomedical Data Science, Stanford University, Stanford, CA, USA

@@

  \textbf{Chun Su}

@@

  Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA

@@

  \textbf{Matthew E. Johnson}
  Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA

@@

  \textbf{Wei-Qi Wei}
  Vanderbilt University Medical Center

@@

  \textbf{Qiping Feng}

@@

  Vanderbilt University Medical Center

@@

  \textbf{Bahram Namjou}
  Cincinnati Children's Hospital Medical Center

@@

  \textbf{Krzysztof Kiryluk}

@@

  Department of Medicine, Division of Nephrology, Vagelos College of Physicians \& Surgeons, Columbia University, New York, New York

@@

  \textbf{Iftikhar Kullo}
  Mayo Clinic

@@

  \textbf{Yuan Luo}
  Northwestern University

@@

  \textbf{Blair D. Sullivan}

@@

  School of Computing, University of Utah, Salt Lake City, UT, USA

@@

  \textbf{Benjamin F. Voight}

@@

  Department of Systems Pharmacology and Translational Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA; Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA; Institute for Translational Medicine and Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA

@@

  \textbf{Carsten Skarke}

@@

  Institute for Translational Medicine and Therapeutics, Department of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA

@@

  \textbf{Marylyn D. Ritchie}

@@

  Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA

@@

  \textbf{Struan F.A. Grant}

@@

  Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA; Division of Endocrinology and Diabetes, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA; Division of Human Genetics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA; Department of Pediatrics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA, 19104, USA; Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA, 19104, USA

@@

  \textbf{Casey S. Greene}

@@

  Center for Health AI, University of Colorado School of Medicine, Aurora, CO 80045, USA; Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA
  · Funded by The Gordon and Betty Moore Foundation (GBMF 4552); The National Human Genome Research Institute (R01 HG010067); The National Cancer Institute (R01 CA237170); The Eunice Kennedy Shriver National Institute of Child Health and Human Development (R01 HD109765)

@@

>>>>

  \textbf{Milton Pividori}\textsuperscript{1,2} \\

@@

@@

  \textbf{Sumei Lu}\textsuperscript{3}

@@

  \textbf{Binglan Li}\textsuperscript{4} \\

@@

@@

  \textbf{Chun Su}\textsuperscript{3} \\

@@

@@

  \textbf{Matthew E. Johnson}\textsuperscript{3}

@@

  \textbf{Wei-Qi Wei}\textsuperscript{5}

@@

  \textbf{Qiping Feng}\textsuperscript{5} \\

@@

@@

  \textbf{Bahram Namjou}\textsuperscript{6}

@@

  \textbf{Krzysztof Kiryluk}\textsuperscript{7} \\

@@

@@

  \textbf{Iftikhar Kullo}\textsuperscript{8}

@@

  \textbf{Yuan Luo}\textsuperscript{9}

@@

  \textbf{Blair D. Sullivan}\textsuperscript{10} \\

@@

@@

  \textbf{Benjamin F. Voight}\textsuperscript{11,12,13} \\

@@

@@

  \textbf{Carsten Skarke}\textsuperscript{13} \\

@@

@@

  \textbf{Marylyn D. Ritchie}\textsuperscript{1} \\

@@

@@

  \textbf{Struan F.A. Grant}\textsuperscript{3,14,15,1} \\

@@

@@

  \textbf{Casey S. Greene}\textsuperscript{16,2} \\

@@

@@

\textsuperscript{1} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{2} Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA.
\textsuperscript{3} Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{4} Department of Biomedical Data Science, Stanford University, Stanford, CA, USA.
\textsuperscript{5} Vanderbilt University Medical Center.
\textsuperscript{6} Cincinnati Children's Hospital Medical Center.
\textsuperscript{7} Department of Medicine, Division of Nephrology, Vagelos College of Physicians \& Surgeons, Columbia University, New York, New York, USA.
\textsuperscript{8} Mayo Clinic.
\textsuperscript{9} Northwestern University.
\textsuperscript{10} School of Computing, University of Utah, Salt Lake City, UT, USA.
\textsuperscript{11} Department of Systems Pharmacology and Translational Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{12} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{13} Institute for Translational Medicine and Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{14} Division of Endocrinology and Diabetes, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{15} Division of Human Genetics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA; Department of Pediatrics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA, 19104, USA.
\textsuperscript{16} Center for Health AI, University of Colorado School of Medicine, Aurora, CO 80045, USA.
